---
title: "gender_analysis_sweets"
output: html_document
date: '2022-10-11'
---

This is an analysis based on the paper "The association of food parenting practices with adolescents’ dietary
behaviors differ by youth gender, but not by parent gender" by Deslippe et al., 2022

```{r message=FALSE, warning=FALSE, results='hide'}
library(vroom)
library(plyr)
library(ggplot2)
library(psych)
library(tidyverse)
library(OpenMx)
library(dplyr)
library(lavaan)
library(semPlot)
library(knitr)
library(kableExtra)
library(GGally)
```

```{r message=FALSE, warning=FALSE, results='hide'}
df<-vroom("/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/final_df.csv")
names(df)
```
## Check normality of sweets
```{r}
hist(df$SWEET_freq) # not normal
min(df$SWEET_freq)
C = 1 #needed to correct for 0s
hist(log10(df$SWEET_freq+C))# good
df$SWEET_log10<-log10(df$SWEET_freq+C)
df$SWEET_log10_scale<-scale(df$SWEET_log10)
hist(df$SWEET_log10_scale)# good
```

# Sweets Models
## Basic model
food security, parent education, child sex, race/ethnicity, independent eating occasions (from covar analysis)
```{r}
m1 <-'SWEET_log10_scale ~ IND_scale + EXP_scale + AVA_log10_scale + MON_scale + AUT_sqrt_scale + MOD_log10_scale + parent_gender  + RACE_ETH + child_SEX + parent_ED + FOOD_SEC_CAT + iEO_log10'
```

## Confirmatory factor analysis 
```{r}
fit1 <- cfa(m1, data = df)
```

## Summary of SSB CFA
```{r}
summary(fit1, standardized=T,rsquare=T)
```
# Summary of CFA

## Visualization of Junk food CFA
```{r}
semPaths(fit1, 'std', layout = 'spring')
```
```{r}
df$parent_gender<-as.ordered(df$parent_gender)
```

## Interaction models
IND_scale, AVA_log10_scal, MON_scale
```{r}
med_IND_ <- "
         # mediator, a path
         parent_gender ~ a*IND_scale+child_SEX+FOOD_SEC_CAT

         # b path
         SWEET_log10_scale ~ b*parent_gender

         # direct effect 
         SWEET_log10_scale ~ cp * IND_scale+child_SEX+FOOD_SEC_CAT

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
"
med_AVA_ <- "
         # mediator, a path
         parent_gender ~ a*AVA_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         SWEET_log10_scale ~ b*parent_gender

         # direct effect 
         SWEET_log10_scale ~ cp * AVA_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "
med_MON_ <- "
         # mediator, a path
         parent_gender ~ a*MON_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         SWEET_log10_scale ~ b*parent_gender

         # direct effect 
         SWEET_log10_scale ~ cp * MON_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "


```



```{r}
set.seed(1234)
```

### Running the models
```{r}
IND_sem <- sem(med_IND_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
AVA_sem <- sem(med_AVA_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
MON_sem <- sem(med_MON_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
```

### Parameter estimates 
```{r}
summary(AVA_sem,  standardized = TRUE) 
summary(IND_sem, standardized = TRUE) 
summary(MON_sem, standardized = TRUE) 
```



# Summary of results
Parent gender is not related to monitoring, availability, nor indulgence

```{r}
save.image(file = "/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/Sweetanalysis.RData")
```

```{r}
load(file = "/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/Sweetanalysis.RData")
```

