---
title: "gender_analysis_final"
output: html_document
date: '2023-6-27'
---

This is an analysis based on the paper "The association of food parenting practices with adolescents’ dietary
behaviors differ by youth gender, but not by parent gender" by Deslippe et al., 2022

Redoing this with Yichen's dataset

```{r message=FALSE, warning=FALSE, results='hide'}
library(vroom)
library(plyr)
library(ggplot2)
library(psych)
library(tidyverse)
library(OpenMx)
library(dplyr)
library(lavaan)
library(semPlot)
library(knitr)
library(kableExtra)
library(GGally)
library(lavaanPlot)
library(lm.beta)
library(modelsummary)

library(boot)
source("~/Downloads/x.boot.r")  

```
# Why
The previous notebook I tried to normalize the data. When I normalized the data the log function actually made everything worse. I am trying to fit the non-normal data this time. 

```{r message=FALSE, warning=FALSE, results='hide'}
df<-vroom("/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/2. data/iEOparent_food.csv")
#names(df)
```

## Mean center
```{r}
scaled_data <- 
  df %>%
  mutate(SSB_freq = scale(SSB, scale = FALSE),
         JUNK_freq = scale(Junk.foods, scale = FALSE),
         SWEET_freq = scale(Sugary.foods, scale = FALSE),
         FV_freq = scale(Fruits.vegetables, scale = FALSE),
         INDULGENCE = scale(Indulgence, scale = FALSE),
         EXPECATION = scale(Expectations, scale = FALSE),
         AVAILABILE = scale(Availability, scale = FALSE),
         MONITORING = scale(Monitoring, scale = FALSE),
         AUTONOMY = scale(Autonomy.Support, scale = FALSE),
         MODELING = scale(Modeling, scale = FALSE)
         )
```

child sex = sex, Q6.3
parent sex = Q6.11
ethnicity = Q6.18
```{r}
summary(as.factor(df$Q6_18))
names(df)
```
# Renaming factors for the tables
```{r}
df_factors<- df %>% 
  mutate(
    Marital_status = fct_recode(as.factor(Marital.status),
                      "Not married" = "1",
                      "Married" = "2"),
    Parent_gender = fct_recode(as.factor(Q6_11),
                      "Male" = "1",
                      "Female" = "2"),
    Ethnicity = fct_recode(as.factor(Q6_18),
                      "Male" = "1",
                      "Female" = "2"),
        Income = fct_recode(as.factor(Q6_17),
                      "Below $25,000" = "1",
                      "$65,000 - $84,999" = "4",
                      "$45,000 - $64,999" = "3",
                      "$85,000 or more" = "5",
                      "$25,000 - $44,999" = "2",
                      "Prefer not to answer" = "6"
                      ),
    child_sex = fct_recode(as.factor(Q6_3),
                      "Male" = "1",
                      "Female" = "2"
                      ),
    education = fct_recode(as.factor(Q6_14),
                      "4-year college, university degree or advanced degree" = "4",
                      "Some college or technical school" = "3",
                      "Received high school diploma or GED" = "2",
                      "Have not completed high school" = "1"
                      
                      ),
    ethnicity = fct_recode(as.factor(Q6_18),
                      "Hispanic or Latinx" = "1",
                      "Not Hispanic or Latinx" = "2"
                      
                      )
  )
```


# Making descriptive table
## Table 1. Sample demographics by parent sex
### Factors
```{r}
#(`Flipper length (mm)` = flipper_length_mm)

datasummary((`Marital status` = Marital_status) + Race+ (`Ethnicity` = ethnicity)+ Income + (`Child sex` = child_sex) + (`Food security` = Food.security) + (`Education` = education) ~ (`Parent gender` = Parent_gender) * Percent("col")+1*Percent("col"),
            data = df_factors,
            output = '/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/table1.docx')
```

### Continuous
```{r}
MeanSD <- function(x) paste0(round(mean(x, na.rm = TRUE),2),'(', round(sd(x, na.rm = TRUE),2), ')')

```

```{r}
datasummary((`Autonomy support` = Autonomy.Support) + Monitoring + Availability + Indulgence + Modeling + Expectations + (`SSB consumption frequency` = SSB) + (`Junk food consumption frequency` = Junk.foods) + (`Fruit and Vegetable consumption frequency` = Fruits.vegetables) + (`Sugary food consumption frequency` = Sugary.foods) + (`Independent eating occassion frequency` = iEO) ~ Parent_gender* (MeanSD) + 1*(MeanSD),
            data = df_factors,
            output = '/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/table1_b.docx')
```

### Check differences
```{r}
summary(df_factors$Parent_gender)
t.test(df_factors$iEO ~ df_factors$Parent_gender)
```
```{r}
mytable <- xtabs(~Parent_gender+Marital.status, data=df_factors)
summary(mytable) # chi-square test of indepedence
```

# Checking regressions against main paper for sanity
```{r}
check_FV_auto<-lm(Fruits.vegetables ~ Autonomy.Support +  Age + Race + Sex + Education + Food.security + Marital.status + iEO, data = df )
summary(check_FV_auto) # b values match the parent reporting parenting practice
```

## Basic model
food security, parent education, child sex, race/ethnicity, independent eating occasions (from covar analysis)
```{r}
mFV <-'FV_freq ~ INDULGENCE + EXPECATION + AVAILABILE + MONITORING + AUTONOMY + MODELING + Q6_11  + Race + Sex + Education + Food.security + iEO'
mSSB <-'SSB_freq ~ INDULGENCE + EXPECATION + AVAILABILE + MONITORING + AUTONOMY + MODELING + Q6_11  + Race + Sex + Education + Food.security + iEO'
mJUNK <-'JUNK_freq ~ INDULGENCE + EXPECATION + AVAILABILE + MONITORING + AUTONOMY + MODELING + Q6_11  + Race + Sex + Education + Food.security + iEO'
mSWEET <-'SWEET_freq ~ INDULGENCE + EXPECATION + AVAILABILE + MONITORING + AUTONOMY + MODELING + Q6_11  + Race + Sex + Education + Food.security + iEO'
```

## Confirmatory factor analysis 
```{r}
fit_FV <- cfa(m1, data = scaled_data)
```
## Refactor levels of race
```{r}
scaled_data$Race <- factor(scaled_data$Race, levels = c("Non-Hispanic White","Non-Hispanic Black", "Asian", "Hispanic", "Other races"))
```


## Summary
Basic models were not significant thus bootstrapping was not required
```{r}
models <- list(
  "Fruits and Vegetables"     = lm(mFV, data = scaled_data),
  "SSB"     = lm(mSSB, data = scaled_data),
  "Junk Foods"     = lm(mJUNK, data = scaled_data),
  "Sugary foods"     = lm(mSWEET, data = scaled_data)
)

modelsummary(
  models,
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}] {stars}",
  statistic = NULL,
  coef_omit = "Intercept",
  coef_rename = c("Q6_11" = "parent sex", "RaceHispanic" = "Hispanic", "RaceNon-Hispanic Black" = "Non-Hispanic Black","RaceNon-Hispanic White" = "Non-Hispanic White", "SexGirl" = "Child girl", "RaceAsian" = "Asian", "RaceOther races" = "Other races"), output = "/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/linearmodels_table.docx")
```
# Summary of CFA
INDULGENCE
MONITORING
iEO
```{r}
parent <- "INDULGENCE"
food <- "FV_freq"
my_string <- sprintf("this is my %s string", new)
```


```{r}
modelr <- function(parent,food){
  sprintf("
         # mediator, a path
         Q6_11 ~ a*%s+iEO

         # b path
        %s ~ b*Q6_11

         # direct effect 
         %s ~ cp * %s+iEO

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
        ",parent,food, food, parent)
}
```

```{r}
check <-sem(modelr("MONITORING","JUNK_freq"), data = scaled_data, estimator = "MLM")
summary(check)
```

```{r}
food_list <- list("FV_freq","SSB_freq","JUNK_freq","SWEET_freq")

```

```{r}
sublist <- list()
for (y in food_list){
    model<-modelr("INDULGENCE",y)
    output <- sem(model, data = scaled_data, estimator = "MLM")
    sublist[[y]] <- list(output)
}
```


```{r}
modelsummary(
  c(sublist$FV_freq,
    sublist$SSB_freq,
    sublist$JUNK_freq, 
    sublist$SWEET_freq),
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}],{stars}",
  statistic = NULL,
  )

```
 
```{r}
sublist2 <- list()
for (y in food_list){
    model<-modelr("MONITORING",y)
    output <- sem(model, data = scaled_data, estimator = "MLM")
    sublist2[[y]] <- list(output)
}
```


```{r}
cm <- c('Q6_11 ~ MONITORING'    = 'Monitoring by parent gender',
        'FV_freq ~ Q6_11' = 'Fruit and vegetable intake by parent gender',
        'FV_freq ~ MONITORING' = 'Fruit and vegetable intake by monitoring',
        'SSB_freq ~ Q6_11' = 'SSB intake by parent gender',
        'SSB_freq ~ MONITORING' = 'SSB intake by monitoring',
        'JUNK_freq ~ Q6_11' = 'Junk food intake by parent gender',
        'JUNK_freq ~ MONITORING	' = 'Junk food intake by monitoring',
        'SWEET_freq ~ Q6_11' = 'Sugary food intake by parent gender',
        'SWEET_freq ~ MONITORING' = 'Sugary food intake by monitoring'
        )

modelsummary(
  c(sublist2$FV_freq,
    sublist2$SSB_freq,
    sublist2$JUNK_freq, 
    sublist2$SWEET_freq),
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}],{stars}",
  statistic = NULL,
  )
```


```{r}
load(file = "/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/gender_analysis.RData")

```


```{r}
#save.image(file = "/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/gender_analysis.RData")
```

