---
title: "gender_analysis_fastfood"
output: html_document
date: '2022-10-11'
---
This is an analysis based on the paper "The association of food parenting practices with adolescents’ dietary
behaviors differ by youth gender, but not by parent gender" by Deslippe et al., 2022

```{r message=FALSE, warning=FALSE, results='hide'}
library(vroom)
library(plyr)
library(ggplot2)
library(psych)
library(tidyverse)
library(OpenMx)
library(dplyr)
library(lavaan)
library(semPlot)
library(knitr)
library(kableExtra)
library(GGally)
library(semTable)
library(kableExtra)
library(gtsummary)
```

```{r message=FALSE, warning=FALSE, results='hide'}
df<-vroom("/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/final_df.csv")
names(df)
```
## Check normality of Fast Food
```{r}
hist(df$FAST_freq) # not normal
min(df$FAST_freq)
C = 1 #needed to correct for 0s
hist(log10(df$FAST_freq+C))# good
df$FAST_log10<-log10(df$FAST_freq+C)
df$FAST_log10_scale<-scale(df$FAST_log10)
hist(df$FAST_log10_scale)# good
```

# Fast Food Models
## Basic model
food security, parent education, child sex, race/ethnicity, independent eating occasions (from covar analysis)
```{r}
m1 <-'FAST_log10_scale ~ IND_scale + EXP_scale + AVA_log10_scale + MON_scale + AUT_sqrt_scale + MOD_log10_scale + parent_gender  + RACE_ETH + child_SEX + parent_ED + FOOD_SEC_CAT + iEO_log10'
```

## Confirmatory factor analysis 
```{r}
fit1 <- cfa(m1, data = df)
summary(fit1)
```

# Summary of CFA
IND_scale,  MON_scale
iEO_log10, FOOD_SEC_CAT
## Visualization of Junk food CFA
```{r}
semPaths(fit1, 'std', layout = 'spring')
```

```{r}
df$parent_gender<-as.ordered(df$parent_gender)
```

## Interaction models
IND_scale, AVA_log10_scal, MON_scale
```{r}
med_IND_ <- "
         # mediator, a path
         parent_gender ~ a*IND_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         FAST_log10_scale ~ b*parent_gender

         # direct effect 
         FAST_log10_scale ~ cp * IND_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
"

med_MON_ <- "
         # mediator, a path
         parent_gender ~ a*MON_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         FAST_log10_scale ~ b*parent_gender

         # direct effect 
         FAST_log10_scale ~ cp * MON_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "
med_AVA_ <- "
         # mediator, a path
         parent_gender ~ a*AVA_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         FAST_log10_scale ~ b*parent_gender

         # direct effect 
         FAST_log10_scale ~ cp * AVA_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "
med_MOD_ <- "
         # mediator, a path
         parent_gender ~ a*MOD_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         FAST_log10_scale ~ b*parent_gender

         # direct effect 
         FAST_log10_scale ~ cp * MOD_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "
```



```{r}
set.seed(1234)
```

### Running the models
```{r}
IND_sem <- sem(med_IND_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
MON_sem <- sem(med_MON_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
AVA_sem<- sem(med_AVA_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
MOD_sem<- sem(med_MOD_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
```

### Parameter estimates 
```{r}
summary(IND_sem, standardized = TRUE) 
summary(MON_sem, standardized = TRUE) 
summary(AVA_sem, standardized = TRUE) 
summary(MOD_sem, standardized = TRUE) 
```
```{r}
library(tidySEM)
library(ggplot2)
library(dplyr)
```
```{r}
graph_sem(model = IND_sem)
```

# Summary of results
## Model with grouping
```{r}
IND_group <- ' 
             # mediator, a path
             parent_gender ~ c(ag1,ag2)*IND_scale+FOOD_SEC_CAT+iEO_log10
             FAST_log10_scale ~ c(bg1,bg2)*parent_gender 
           
             # direct effect
             FAST_log10_scale ~  c(cg1, cg2)*IND_scale+FOOD_SEC_CAT+iEO_log10

           # indirect effect (a*b)
             abg1 := ag1*bg1 #group 1
             abg2 := ag2*bg2 #group 2

           # total effect
             totalg1 := cg1 + (ag1*bg1)
             totalg2 := cg2 + (ag2*bg2)
         '
```


## Running group models
```{r}
fit_group_IND <- sem(IND_group, data = df, group="child_SEX", 
                 se="boot", bootstrap=50, meanstructure = TRUE, estimator = "DWLS")
```



```{r}
summary(fit_group_IND, fit.measures=T, standardized=T, ci=TRUE)
```

```{r}
all.constraints<- 'ag1 == ag2
                  bg1 == bg2
                  cg1 == cg2'
```


```{r}
lavTestWald(fit_group_IND, #the name of the Lavaan 'fitted' object
            constraints = all.constraints) #the name of our previously specified paths that we would like to test
```

```{r}
#save.image(file = "/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/Fastfoodanalysis.RData")
```

```{r}
load(file = "/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/Fastfoodanalysis.RData")
```

