---
title: "gender_analysis_junk_food"
output: html_document
date: '2022-10-11'
---

This is an analysis based on the paper "The association of food parenting practices with adolescents’ dietary
behaviors differ by youth gender, but not by parent gender" by Deslippe et al., 2022

```{r message=FALSE, warning=FALSE, results='hide'}
library(vroom)
library(plyr)
library(ggplot2)
library(psych)
library(tidyverse)
library(OpenMx)
library(dplyr)
library(lavaan)
library(semPlot)
library(knitr)
library(kableExtra)
library(GGally)
```

```{r message=FALSE, warning=FALSE, results='hide'}
df<-vroom("/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/final_df.csv")
#df$parent_gender<-as.factor(df$parent_gender)
#df$child_SEX<-as.factor(df$child_SEX)
```
## Check normality of junk food
```{r}
hist(df$JUNK_freq) # not normal
min(df$JUNK_freq)
C = 1 #needed to correct for 0s
hist(log10(df$JUNK_freq+C))# good
df$JUNK_log10<-log10(df$JUNK_freq+C)
df$JUNK_log10_scale<-scale(df$JUNK_log10)
hist(df$JUNK_log10_scale)# good
```

# Junk food Models
## Basic model
food security, parent education, child sex, race/ethnicity, independent eating occasions (from covar analysis)
```{r}
m1 <-'JUNK_log10_scale ~ IND_scale + EXP_scale + AVA_log10_scale + MON_scale + AUT_sqrt_scale + MOD_log10_scale + parent_gender  + RACE_ETH + child_SEX + parent_ED + FOOD_SEC_CAT + iEO_log10'
```

## Confirmatory factor analysis 
```{r}
fit1 <- cfa(m1, data = df)
```

## Summary of SSB CFA
```{r}
summary(fit1, standardized=T,rsquare=T)
```
# Summary of CFA
IND_scale, AVA_log10_scal, MON_scale
FOOD_SEC_CAT, iEO_log10
## Visualization of Junk food CFA
```{r}
semPaths(fit1, 'std', layout = 'spring')
```
```{r}
df$parent_gender<-as.ordered(df$parent_gender)
```

## Interaction models
IND_scale, AVA_log10_scal, MON_scale

```{r}
med_IND_ <- "
         # mediator, a path
         parent_gender ~ a*IND_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         JUNK_log10_scale ~ b*parent_gender

         # direct effect 
         JUNK_log10_scale ~ cp * IND_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
"
med_AVA_ <- "
         # mediator, a path
         parent_gender ~ a*AVA_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         JUNK_log10_scale ~ b*parent_gender

         # direct effect 
         JUNK_log10_scale ~ cp * AVA_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "
med_MON_ <- "
         # mediator, a path
         parent_gender ~ a*MON_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         JUNK_log10_scale ~ b*parent_gender

         # direct effect 
         JUNK_log10_scale ~ cp * MON_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "
```



```{r}
set.seed(1234)
```

### Running the models
```{r}
IND_sem <- sem(med_IND_, data = df, se = "bootstrap", bootstrap = 5, estimator = "DWLS")
AVA_sem <- sem(med_AVA_, data = df, se = "bootstrap", bootstrap = 5, estimator = "DWLS")
MON_sem <- sem(med_MON_, data = df, se = "bootstrap", bootstrap = 5, estimator = "DWLS")
```

### Parameter estimates 
```{r}
summary(AVA_sem,  standardized = TRUE) 
summary(IND_sem, standardized = TRUE) 
summary(MON_sem, standardized = TRUE) 
```
```{r}
makincopies<-function(X, Y){
  sumsum<-describeBy(X, Y)
  test<-map2_dfr(as.data.frame(sumsum[1]), as.data.frame(sumsum[2]), ~ tibble(A = .x, B = .y))
  nms<-c('var','n', 'mean','sd','median','trimmed','mad','min','max','range','skew','kurtosis','se')
  df_transpose = as.data.frame(t(test))
  colnames(df_transpose)<-nms
  df_transpose<-rownames_to_column(df_transpose)
  return(df_transpose)
}
cbPalette <- c( "#6D8DF3","#CC4F7E")
summarized_df<-makincopies(df$IND_scale, df$parent_gender)
summarized_df2<-makincopies(df$JUNK_log10_scale, df$parent_gender)
```

A = male
B = Female
```{r}
ggplot(summarized_df, aes(x=rowname, y=mean, fill = rowname)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+ labs(title = "Indulgence by parent gender", x = "Parent gender", y = "Indulgence (scaled)") + scale_fill_manual(values=cbPalette) + scale_x_discrete(labels=c("A" = "Male", "B" = "Female")) + theme_classic()+ theme(legend.position = "none")
```

```{r}
ggplot(summarized_df2, aes(x=rowname, y=mean, fill = rowname)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+ labs(title = "Junk food intake intake by parent gender", x = "Parent gender", y = "Junk food intake intake (log10 transformed and scaled)") + scale_fill_manual(values=cbPalette) + scale_x_discrete(labels=c("A" = "Male", "B" = "Female")) + theme_classic()+ theme(legend.position = "none")
```

0 = male
1 = female
```{r}

ggplot(df, aes(x=IND_scale, y=JUNK_log10_scale, color=parent_gender)) +geom_smooth(method=lm)  +
    geom_point(shape=1) + theme_classic() + labs(title = "Interaction of parent gender on indulgence and junk food intake", x = "Indulgence (scaled)", y = "Junk food intake (log10 transformed and scaled)", color = "Parent gender \n0 is male, 1 is female") + scale_colour_manual(values=cbPalette)

```

```{r}
labels <- list(child_SEX = "child sex", IND_scale = "Indulgence", iEO_log10 = "Independent eating occasions", parent_gender = "Parent gender", FOOD_SEC_CAT = "Food security", JUNK_log10_scale = "Junk food intake")

lavaanPlot(model = IND_sem,labels = labels, node_options = list(shape = "box", fontname = "Helvetica"), edge_options = list(color = "grey"), coefs = T, sig = .1, stand = TRUE)
```


# Summary of results
Parent gender is not related to monitoring, availability, nor indulgence

# Is mediation (parental gender) moderated by child sex (female < male) ?

## Model with grouping
```{r}
MON_group <- ' 
             # mediator, a path
             parent_gender ~ c(ag1,ag2)*MON_scale+FOOD_SEC_CAT+iEO_log10
             JUNK_log10_scale ~ c(bg1,bg2)*parent_gender 
           
             # direct effect
             JUNK_log10_scale ~  c(cg1, cg2)*MON_scale+FOOD_SEC_CAT+iEO_log10

           # indirect effect (a*b)
             abg1 := ag1*bg1 #group 1
             abg2 := ag2*bg2 #group 2

           # total effect
             totalg1 := cg1 + (ag1*bg1)
             totalg2 := cg2 + (ag2*bg2)
         '
```


## Running group models
```{r}
fit_group_MON <- sem(MON_group, data = df, group="child_SEX", 
                 se="boot", bootstrap=5000, meanstructure = TRUE, estimator = "DWLS")
```

```{r}
summary(fit_group_MON, fit.measures=T, standardized=T, ci=TRUE)
```

```{r}
all.constraints<- 'ag1 == ag2
                  bg1 == bg2
                  cg1 == cg2'
```


```{r}
lavTestWald(fit_group_MON, #the name of the Lavaan 'fitted' object
            constraints = all.constraints) #the name of our previously specified paths that we would like to test
```
# Summary of moderation results
Although parent gender doesn't mediate junk food, it appears that child sex trends to moderate the effect at least in terms of monitoring.

```{r}
#save.image(file = "/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/Junkanalysis.RData")
```

```{r}
load(file = "/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/Junkanalysis.RData")
```

