---
title: "Gendered perspective paper - SSB analysis"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
This is an analysis based on the paper "The association of food parenting practices with adolescents’ dietary
behaviors differ by youth gender, but not by parent gender" by Deslippe et al., 2022

```{r message=FALSE, warning=FALSE, results='hide'}
library(vroom)
library(plyr)
library(ggplot2)
library(psych)
library(tidyverse)
library(OpenMx)
library(dplyr)
library(lavaan)
library(semPlot)
library(knitr)
library(kableExtra)
library(GGally)
```

```{r message=FALSE, warning=FALSE, results='hide'}
df<-vroom("~/University of Wyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/final_df.csv")
df$parent_gender<-as.factor(df$parent_gender)
df$child_SEX<-as.factor(df$child_SEX)
```
# SSB Models
## Basic model
```{r}
m1 <-'SSB_sqrt_scale ~ IND_scale + EXP_scale + AVA_log10_scale + MON_scale + AUT_sqrt_scale + MOD_log10_scale + parent_gender + parent_ED + INCOME + RACE_ETH + child_SEX'
```

## Confirmatory factor analysis 
```{r}
fit1 <- cfa(m1, data = df)
```

## Summary of SSB CFA
```{r}
summary(fit1, standardized=T,rsquare=T)
```
## Visualization of SSB CFA
```{r}
semPaths(fit1, 'std', layout = 'spring')
```
# Summary of CFA
Indulgence, monitoring related to SSB

## Interaction models
```{r}
med_IND_ <- "# mediator, a path
         parent_gender ~ a*IND_scale

         # b path
         SSB_sqrt_scale ~ b*parent_gender

         # direct effect 
         SSB_sqrt_scale ~ cp * IND_scale

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
"

med_MON_ <- "# a path
         parent_gender ~ a * MON_scale 

         # b path
         SSB_sqrt_scale ~ b * parent_gender

         # c prime path 
         SSB_sqrt_scale ~ cp * MON_scale 

         # indirect and total effects
         ab := a * b
         total := cp + (a*b)
"
```

```{r}
set.seed(1234)
```

### Running the models
```{r}
df$parent_gender<-as.ordered(df$parent_gender)
IND_sem <- sem(med_IND_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
MON_sem <- sem(med_MON_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
```

### Parameter estimates for indulgence
```{r}
parameterestimates(IND_sem, boot.ci.type = "bca.simple", standardized = TRUE) 
```

### Parameter estimates for monitoring
```{r}
parameterestimates(MON_sem, boot.ci.type = "bca.simple", standardized = TRUE) 
```

# Summary of results
* No mediation for indulgence based on parent gender
* Parent gender appear to trend toward mediating the relationship between ssb intake and parental monitoring (est = 0.017, CI= -0.001:0.042)
Will only carry forward monitoring

# Is mediation (parental gender) moderated by child sex (female < male) ?

## Model with grouping
```{r}
MON_group <- ' 
             # mediator, a path
             parent_gender ~ c(ag1,ag2)*MON_scale
             SSB_sqrt_scale ~ c(bg1,bg2)*parent_gender 
           
             # direct effect
             SSB_sqrt_scale ~  c(cg1, cg2)*MON_scale

           # indirect effect (a*b)
             abg1 := ag1*bg1 #group 1
             abg2 := ag2*bg2 #group 2

           # total effect
             totalg1 := cg1 + (ag1*bg1)
             totalg2 := cg2 + (ag2*bg2)
         '
```


## Running group models
```{r}
fit_group_MON <- sem(MON_group, data = df, group="child_SEX", 
                 se="boot", bootstrap=5000, meanstructure = TRUE, estimator = "DWLS")
```

```{r}
summary(fit_group_MON, fit.measures=T, standardized=T, ci=TRUE)
```

```{r}
all.constraints<- 'ag1 == ag2
                  bg1 == bg2
                  cg1 == cg2'
```


```{r}
lavTestWald(fit_group_MON, #the name of the Lavaan 'fitted' object
            constraints = all.constraints) #the name of our previously specified paths that we would like to test
```
# Summary of moderation results
Child sex does not moderate the relationship between monitoring by parental gender and SSB intake 

```{r}
#save.image(file = "~/University of Wyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/SSBanalysis.RData")
```

