---
title: "Gendered perspective paper - cleaning data"
output: html_notebook
---

```{r}
library(vroom)
library(plyr)
library(ggplot2)
library(psych)
library(tidyverse)
library(OpenMx)
library(dplyr)
```

# Read in the data
```{r}
df<-vroom("~/University of Wyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/Qualtrics+Pilot-Actual+2020-Parent-Child+Dyad+Survey_December+21,+2021_09.21.csv")
df<-df[-c(1), ] # remove extra header row
head(df[, c(15:203)])
```
```{r}
df<-df[,c(24,28, 36:203, 274:308,353:358, 361, 368:371, 342:348) ]  # variables of interest
```
# Diet data
Cols 42-203
From table 1 FLASHE guide - Drinks into drinks per day
From table 2

## SSB
soda + energy drinks + sweetened
fruit drinks + sports drinks
```{r SSB conversion}
df0<-df %>%
  mutate(across(c('Q2.6','Q2.12','Q2.18','Q2.24','Q2.30','Q2.36','Q2.13','Q2.14','Q2.15','Q2.16','Q2.17'),
                factor))

df1<-df0 %>%
  mutate_at(c('Q2.6','Q2.7','Q2.8','Q2.9','Q2.10','Q2.11'), funs(recode(.,
                              'I did not drink sweetened fruit drinks during the past 7 days' = 0,                
                              'I did not drink sweetened fruit drinks when my main caregiver was not around' = 0,
                              '1 \xd0 3 times in the past 7 days' = 0.29,
                              '4 \xd0 6 times in the past 7 days' = 0.71,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3)))%>%
  mutate_at(c('Q2.12','Q2.13','Q2.14','Q2.15','Q2.16','Q2.17'), funs(recode(.,
                              'I did not drink 100% pure fruit juice during the past 7 days' = 0,
                              'I did not drink 100% pure fruit juice when my main caregiver was not around' = 0,
                              '1 \xd0 3 times in the past 7 days' = 0.29,
                              '4 \xd0 6 times in the past 7 days' = 0.71,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3)))%>%
  mutate_at(c('Q2.18','Q2.19','Q2.20','Q2.21','Q2.22','Q2.23'), funs(recode(.,
                              'I did not drink soda during the past 7 days' = 0,
                              'I did not drink soda when my main caregiver was not around' = 0,
                              '1 \xd0 3 times in the past 7 days' = 0.29,
                              '4 \xd0 6 times in the past 7 days' = 0.71,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3)))%>%
  mutate_at(c('Q2.24','Q2.25','Q2.26','Q2.27','Q2.28','Q2.29'), funs(recode(.,
                              'I did not drink energy drinks during the past 7 days' = 0,
                              'I did not drink energy drinks when my main caregiver was not around' = 0,
                              '1 \xd0 3 times in the past 7 days' = 0.29,
                              '4 \xd0 6 times in the past 7 days' = 0.71,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3)))%>%
  mutate_at(c('Q2.30','Q2.31','Q2.32','Q2.33','Q2.34','Q2.35'), funs(recode(.,
                              'I did not drink sports drinks during the past 7 days' = 0,
                              'I did not drink sports drinks when my main caregiver was not around' = 0,
                              '1 \xd0 3 times in the past 7 days' = 0.29,
                              '4 \xd0 6 times in the past 7 days' = 0.71,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3)))%>%
  mutate_at(c('Q2.36','Q2.37','Q2.38','Q2.39','Q2.40','Q2.41'), funs(recode(.,
                              'I did not drink water during the past 7 days' = 0,
                              'I did not drink water when my main caregiver was not around' = 0,
                              '1 \xd0 3 times in the past 7 days' = 0.29,
                              '4 \xd0 6 times in the past 7 days' = 0.71,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3)))

```

## Junk Foods
candy/chocolate + cookies/cake +
potato chips + fried potatoes +
frozen desserts
```{r Junk food conversion}
df2<-df1 %>%
  mutate_at(c('Q2.133','Q2.134','Q2.135','Q2.136','Q2.137','Q2.138'), funs(recode(.,
                              'I did not eat candy or chocolate during the past 7 days' = 0,                                         
                              'I did not eat candy or chocolate when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.139','Q2.140','Q2.141','Q2.142','Q2.143','Q2.144'), funs(recode(.,
                              'I did not eat any of these during the past 7 days' = 0,                                         
                              'I did not eat any of these when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.145','Q2.146','Q2.147','Q2.148','Q2.149','Q2.150'), funs(recode(.,
                              'I did not eat frozen desserts during the past 7 days' = 0,                                         
                              'I did not eat frozen desserts when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.151','Q2.152','Q2.153','Q2.154','Q2.155','Q2.156'), funs(recode(.,
                              'I did not eat chips during the past 7 days' = 0,                                         
                              'I did not eat chips when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.61','Q2.62','Q2.63','Q2.64','Q2.65','Q2.66'), funs(recode(.,
                              'I did not eat fried potatoes during the past 7 days' = 0,                                         
                              'I did not eat fried potatoes when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) 

```
## Sugary Foods
frozen dessert + cookies/cake +
candy/chocolate + sugary cereal
```{r sugar cereal conv}
df3<-df2 %>%
  mutate_at(c('Q2.157','Q2.158','Q2.159','Q2.160','Q2.161','Q2.162'), funs(recode(.,
                              'I did not eat sugary cereals during the past 7 days' = 0,                                         
                              'I did not eat sugary cereals when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) 
summary(as.factor(df2$Q2.158))
```
## Fast/Convenience Foods
fried potatoes + fried chicken +
pizza + tacos + burgers + heat and serve
```{r convenience foods conv}
df4<-df3 %>%
  mutate_at(c('Q2.115','Q2.116','Q2.117','Q2.118','Q2.119','Q2.120'), funs(recode(.,
                              'I did not eat fried chicken during the past 7 days' = 0,                                         
                              'I did not eat fried chicken when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.109','Q2.110','Q2.111','Q2.112','Q2.113','Q2.114'), funs(recode(.,
                              'I did not eat hamburgers or cheeseburgers during the past 7 days' = 0,                                       
                              'I did not eat hamburgers or cheeseburgers when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.97','Q2.98','Q2.99','Q2.100','Q2.101','Q2.102'), funs(recode(.,
                              'I did not eat foods that you heat and serve during the past 7 days' = 0,                                     
                              'I did not eat foods that you heat and serve when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3)))%>%
  mutate_at(c('Q2.91','Q2.92','Q2.93','Q2.94','Q2.95','Q2.96'), funs(recode(.,
                              'I did not eat these dishes food during the past 7 days' = 0,                                     
                              'I did not eat these dishes when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3)))%>%
  mutate_at(c('Q2.85','Q2.86','Q2.87','Q2.88','Q2.89','Q2.90'), funs(recode(.,
                              'I did not eat pizza during the past 7 days' = 0,                                     
                              'I did not eat pizza when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3)))
```
## Fruits and vegetables
100% fruit juice + fruit + green salad
+ other non-fried vegetables +
cooked beans + other potatoes
```{r fruit+veg conversion}
df5<-df4 %>%
  mutate_at(c('Q2.49','Q2.50','Q2.51','Q2.52','Q2.53','Q2.54'), funs(recode(.,
                              'I did not eat fruit during the past 7 days' = 0,                                   
                              'I did not eat fruit when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.55','Q2.56','Q2.57','Q2.58','Q2.59','Q2.60'), funs(recode(.,
                              'I did not eat green salad during the past 7 days' = 0,                             
                              'I did not eat green salad when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.67','Q2.68','Q2.69','Q2.70','Q2.71','Q2.72'), funs(recode(.,
                              'I did not eat non-fried potatoes during the past 7 days' = 0,                      
                              'I did not eat non-fried potatoes when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.73','Q2.74','Q2.75','Q2.76','Q2.77','Q2.78'), funs(recode(.,
                              'I did not eat non-fried vegetables during the past 7 days' = 0,                    
                              'I did not eat non-fried vegetables when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) %>%
  mutate_at(c('Q2.79','Q2.80','Q2.81','Q2.82','Q2.83','Q2.84'), funs(recode(.,
                              'I did not eat cooked beans during the past 7 days' = 0,                    
                              'I did not eat cooked beans when my main caregiver was not around' = 0,
                              '1-3 times in the past 7 days' = 0.29,
                              '4-6 times in the past 7 days' = 0.71,
                              '1 time per day' = 1,
                              '2 times per day' = 2,
                              '3 or more times per day' = 3))) 
```
# Freq total
```{r frequencies}
df6<-df5 %>%
  mutate(SSB_freq = rowSums(across(c('Q2.6','Q2.12','Q2.18','Q2.24','Q2.30')))) %>% 
  mutate(JUNK_freq = rowSums(across(c('Q2.133','Q2.139','Q2.145','Q2.151','Q2.61')))) %>% 
  mutate(SWEET_freq = rowSums(across(c('Q2.157','Q2.133','Q2.139','Q2.145'))))%>% 
  mutate(FAST_freq = rowSums(across(c('Q2.115','Q2.109','Q2.97','Q2.91','Q2.85'))))%>% 
  mutate(FV_freq = rowSums(across(c('Q2.49','Q2.55','Q2.67','Q2.73','Q2.79'))))

summary(df6$FV_freq)
```

# Need to create a food parenting practice constructs
See codebook
```{r recode parenting to numeric}
df7<-df6 %>%
  mutate_at(c('Q5.5_1','Q5.5_2','Q5.5_3','Q5.5_4','Q5.6_1','Q5.6_2','Q5.6_3','Q5.6_4','Q5.7_1','Q5.7_2','Q5.7_3','Q5.7_4','Q5.8_1','Q5.8_2','Q5.8_3','Q5.8_4','Q5.9_1','Q5.9_2','Q5.9_3','Q5.9_4','Q4.10_19','Q3.14_3','Q4.10_20','Q4.10_21','Q4.10_22','Q2.11_18','Q4.11_19','Q4.11_20','Q4.12_22','Q4.12_19','Q4.12_20','Q5.13_1','Q5.13_2','Q5.13_3'), funs(recode(.,                                                                                                                  'Never' = 1,'Sometimes' = 2,'About half the time' = 3,'Most of the time' = 4,'Always' = 5
                  ))) 
```



```{r mean parent factors}
df8<-df7 %>%
  mutate(INDULGENCE = rowMeans(across(c('Q5.5_1','Q5.6_1', 'Q5.6_3','Q5.7_4','Q4.10_19','Q4.12_20')))) %>% 
  mutate(EXPECATION = rowMeans(across(c('Q5.5_2','Q5.7_2','Q4.10_20')))) %>% 
  mutate(AVAILABILE = rowMeans(across(c('Q5.5_4','Q5.9_1','Q5.9_3','Q4.10_22','Q4.12_19'))))%>% 
  mutate(MONITORING = rowMeans(across(c('Q5.5_3','Q5.7_1','Q5.7_3','Q5.8_4','Q5.9_4','Q5.13_1','Q5.13_2'))))%>% 
  mutate(AUTONOMY = rowMeans(across(c('Q5.6_2','Q5.6_4','Q5.8_1','Q5.8_3','Q3.14_3','Q4.10_21','Q2.11_18','Q4.11_19','Q5.13_3'))))%>%
  mutate(MODELING = rowMeans(across(c('Q5.8_2','Q5.9_2','Q4.12_22'))))
```
## Parent gender
```{r}
summary(as.factor(df8$Q6.11))
df8$parent_gender<-as.factor(df8$Q6.11)
```

## Education
```{r}
summary(as.factor(df8$Q6.14))
df8$parent_ED<-as.factor(df8$Q6.14)
```

## Income
```{r}
summary(as.factor(df8$Q6.17))
df8$INCOME<-as.factor(df8$Q6.17)
```

## Race ethnicity
```{r}
summary(as.factor(df8$Q1.21_4))
df9<-df8 %>% 
  unite("RACE_ETH", Q1.21_1:Q1.21_6, remove = FALSE,na.rm = TRUE)
summary(as.factor(df9$RACE_ETH))
```

## Adolescent age
```{r}
summary(as.factor(df9$Q6.2))

df10<-df9 %>%
  mutate_at(c('Q6.2'), funs(recode(.,                                                                                                                  '11 years' = 11,'12 years' = 12,'13 years' = 13,'14 years' = 14
                  ))) 

df10$child_AGE<-df10$Q6.2
```

```{r}
summary(as.factor(df10$Q6.3))
df10$child_SEX<-as.factor(df10$Q6.3)
```

```{r}
interest<-c("SSB_freq","JUNK_freq","SWEET_freq","FAST_freq","FV_freq","INDULGENCE","EXPECATION", "AVAILABILE","MONITORING",    "AUTONOMY","MODELING","parent_gender", "parent_ED","INCOME","child_SEX","RACE_ETH")
final_df<-df10[interest]
head(final_df)
```

```{r}
names(final_df)
```

```{r}

hist(sqrt(final_df$SSB_freq)) # not normal, sqrt helps
final_df$SSB_sqrt<-sqrt(final_df$SSB_freq)
hist(final_df$INDULGENCE)
hist(log10(6-final_df$EXPECATION)) # could be better, log10 and subtracting largest
final_df$EXP_log10<-log10(6-final_df$EXPECATION)
#summary(final_df$EXPECATION)
hist(log10(6-final_df$AVAILABILE))# not normal, log 10 and subtracting largest
final_df$AVA_log10<-log10(6-final_df$AVAILABILE)
hist(final_df$MONITORING)
hist(sqrt(6-final_df$AUTONOMY))# not normal, sqty and subtracting largest
final_df$AUT_sqrt<-sqrt(6-final_df$AUTONOMY)
hist(log10(6-final_df$MODELING))# could be better, log 10 and subtracting the largest
final_df$MOD_log10<-log10(6-final_df$MODELING)
```


```{r}
names(final_df)
final_df$SSB_sqrt_scale<-as.numeric(scale(final_df$SSB_sqrt, scale = F))
final_df$MOD_log10_scale<-as.numeric(scale(final_df$MOD_log10, scale = F))
final_df$AUT_sqrt_scale<-as.numeric(scale(final_df$AUT_sqrt, scale = F))
final_df$AVA_log10_scale<-as.numeric(scale(final_df$AVA_log10, scale = F))
final_df$EXP_log10_scale<-as.numeric(scale(final_df$EXP_log10, scale = F))
final_df$IND_scale<-as.numeric(scale(final_df$INDULGENCE, scale = F))
final_df$EXP_scale<-as.numeric(scale(final_df$EXPECATION, scale = F))
final_df$MON_scale<-as.numeric(scale(final_df$MONITORING, scale = F))
summary(final_df)
```


```{r}
write.table(final_df, "~/University of Wyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/final_df.csv", row.names = F, sep = ",")
```

```{r}
#load(file = "~/University of Wyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/cleaning.RData")
```





```{r}
#save.image(file = "~/University of Wyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/cleaning.RData")
```

