---
title: "gender_analysis_fruitveg"
output: html_document
date: '2022-10-12'
---

This is an analysis based on the paper "The association of food parenting practices with adolescents’ dietary
behaviors differ by youth gender, but not by parent gender" by Deslippe et al., 2022

```{r message=FALSE, warning=FALSE, results='hide'}
library(vroom)
library(plyr)
library(ggplot2)
library(psych)
library(tidyverse)
library(OpenMx)
library(dplyr)
library(lavaan)
library(semPlot)
library(knitr)
library(kableExtra)
library(GGally)
library(lavaanPlot)
```

```{r message=FALSE, warning=FALSE, results='hide'}
df<-vroom("/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/final_df.csv")
names(df)
```
## Check normality of Fast Food
```{r}
str(df)
hist(df$FV_freq) # not normal
min(df$FV_freq)
C = 1 #needed to correct for 0s
hist(log10(df$FV_freq+C))# good
df$FV_log10<-log10(df$FV_freq+C)
df$FV_log10_scale<-scale(df$FV_log10)
hist(df$FV_log10_scale)# good
```

# Fast Food Models
## Basic model
food security, parent education, child sex, race/ethnicity, independent eating occasions (from covar analysis)
```{r}
m1 <-'FV_log10_scale ~ IND_scale + EXP_scale + AVA_log10_scale + MON_scale + AUT_sqrt_scale + MOD_log10_scale + parent_gender  + RACE_ETH + child_SEX + parent_ED + FOOD_SEC_CAT + iEO_log10'
```

## Confirmatory factor analysis 
```{r}
fit1 <- cfa(m1, data = df)
```

## Summary of SSB CFA
```{r}
summary(fit1, standardized=T,rsquare=T)
```
# Summary of CFA
IND_scale, MON_scale, MOD_log10_scal, parent_ED, FOOD_SEC_CAT, iEO_log10 
## Visualization of Junk food CFA
```{r}
semPaths(fit1, 'std', layout = 'spring')
```
```{r}
df$parent_gender<-as.ordered(df$parent_gender)
```

## Interaction models
IND_scale, AVA_log10_scal, MON_scale
```{r}
med_MOD_ <- "
         # mediator, a path
         parent_gender ~ a*MOD_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         FV_log10_scale ~ b*parent_gender

         # direct effect 
         FV_log10_scale ~ cp * MOD_log10_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "
med_MON_ <- "
         # mediator, a path
         parent_gender ~ a*MON_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         FV_log10_scale ~ b*parent_gender

         # direct effect 
         FV_log10_scale ~ cp * MON_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "
med_IND_ <- "
         # mediator, a path
         parent_gender ~ a*IND_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # b path
         FV_log10_scale ~ b*parent_gender

         # direct effect 
         FV_log10_scale ~ cp * IND_scale+child_SEX+FOOD_SEC_CAT+iEO_log10

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
         "
```



```{r}
set.seed(1234)
```

### Running the models
```{r}
IND_sem2 <- sem(med_IND_2, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")

IND_sem <- sem(med_IND_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
MON_sem <- sem(med_MON_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
MOD_sem <- sem(med_MOD_, data = df, se = "bootstrap", bootstrap = 5000, estimator = "DWLS")
```


### Parameter estimates 
```{r}
summary(IND_sem, standardized = TRUE) 
summary(MON_sem, standardized = TRUE) 
summary(MOD_sem, standardized = TRUE) 
```
```{r}
makincopies<-function(X, Y){
  sumsum<-describeBy(X, Y)
  test<-map2_dfr(as.data.frame(sumsum[1]), as.data.frame(sumsum[2]), ~ tibble(A = .x, B = .y))
  nms<-c('var','n', 'mean','sd','median','trimmed','mad','min','max','range','skew','kurtosis','se')
  df_transpose = as.data.frame(t(test))
  colnames(df_transpose)<-nms
  df_transpose<-rownames_to_column(df_transpose)
  return(df_transpose)
}
cbPalette <- c( "#6D8DF3","#CC4F7E")
summarized_df<-makincopies(df$IND_scale, df$parent_gender)
summarized_df2<-makincopies(df$FV_log10, df$parent_gender)
```

A = male
B = Female
```{r}
ggplot(summarized_df, aes(x=rowname, y=mean, fill = rowname)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+ labs(title = "Indulgence by parent gender", x = "Parent gender", y = "Indulgence (scaled)") + scale_fill_manual(values=cbPalette) + scale_x_discrete(labels=c("A" = "Male", "B" = "Female")) + theme_classic()+ theme(legend.position = "none")
```
```{r}
ggplot(summarized_df2, aes(x=rowname, y=mean, fill = rowname)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+ labs(title = "Fruit and vegetable intake by parent gender", x = "Parent gender", y = "Fruit and vegetable intake (log10 transformed and scaled)") + scale_fill_manual(values=cbPalette) + scale_x_discrete(labels=c("A" = "Male", "B" = "Female")) + theme_classic()+ theme(legend.position = "none")
```
0 = male
1 = female
```{r}
cbPalette <- c( "#6D8DF3","#CC4F7E")

ggplot(df, aes(x=IND_scale, y=FV_log10_scale, color=parent_gender)) +geom_smooth(method=lm)  +
    geom_point(shape=1) + theme_classic() + labs(title = "Interaction of parent gender on indulgence and fruit and vegetable intake", x = "Indulgence (scaled)", y = "Fruit and vegetable intake (log10 transformed and scaled)", color = "Parent gender \n0 is male, 1 is female") + scale_colour_manual(values=cbPalette)

```

```{r}
labels <- list(child_SEX = "child sex", IND_scale = "Indulgence", iEO_log10 = "Independent eating occasions", parent_gender = "Parent gender", FOOD_SEC_CAT = "Food security", FV_log10_scale = "Fruit and veggie intake")

lavaanPlot(model = IND_sem,labels = labels, node_options = list(shape = "box", fontname = "Helvetica"), edge_options = list(color = "grey"), coefs = T, sig = .1, stand = TRUE)
```



# Summary of results
* Indulgence related (0.06)
* Indulgence trending
## Model with grouping
```{r}
IND_group <- ' 
             # mediator, a path
             parent_gender ~ c(ag1,ag2)*IND_scale+FOOD_SEC_CAT+iEO_log10
             FV_log10_scale ~ c(bg1,bg2)*parent_gender 
           
             # direct effect
             FV_log10_scale ~  c(cg1, cg2)*IND_scale+FOOD_SEC_CAT+iEO_log10

           # indirect effect (a*b)
             abg1 := ag1*bg1 #group 1
             abg2 := ag2*bg2 #group 2

           # total effect
             totalg1 := cg1 + (ag1*bg1)
             totalg2 := cg2 + (ag2*bg2)
         '
```


## Running group models
```{r}
fit_group_IND <- sem(IND_group, data = df, group="child_SEX", 
                 se="boot", bootstrap=5000, meanstructure = TRUE, estimator = "DWLS")
```

```{r}
fit_group_IND <- sem(IND_group, data = df, group="child_SEX", 
                 se="boot", bootstrap=5000, meanstructure = TRUE, estimator = "DWLS")
```

```{r}
summary(fit_group_IND, fit.measures=T, standardized=T, ci=TRUE)
```

```{r}
all.constraints<- 'ag1 == ag2
                  bg1 == bg2
                  cg1 == cg2'
```


```{r}
lavTestWald(fit_group_IND, #the name of the Lavaan 'fitted' object
            constraints = all.constraints) #the name of our previously specified paths that we would like to test
```
* Child gender is not related



```{r}
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}
```

```{r}
normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
    library(plyr)

    # Measure var on left, idvar + between vars on right of formula.
    data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
     .fun = function(xx, col, na.rm) {
        c(subjMean = mean(xx[,col], na.rm=na.rm))
      },
      measurevar,
      na.rm
    )

    # Put the subject means with original data
    data <- merge(data, data.subjMean)

    # Get the normalized data in a new column
    measureNormedVar <- paste(measurevar, "_norm", sep="")
    data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                               mean(data[,measurevar], na.rm=na.rm)

    # Remove this subject mean column
    data$subjMean <- NULL

    return(data)
}
```

```{r}
## Summarizes data, handling within-subjects variables by removing inter-subject variability.
## It will still work if there are no within-S variables.
## Gives count, un-normed mean, normed mean (with same between-group mean),
##   standard deviation, standard error of the mean, and confidence interval.
## If there are within-subject variables, calculate adjusted values using method from Morey (2008).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   withinvars: a vector containing names of columns that are within-subjects variables
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
    FUN=is.factor, FUN.VALUE=logical(1))

  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }

  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL

  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")

  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                           FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor

  # Combine the un-normed means with the normed results
  merge(datac, ndatac)
}
```


```{r}
#save.image(file = "/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/FVanalysis.RData")
```

```{r}
load(file = "/Users/gracer/Library/CloudStorage/OneDrive-SharedLibraries-UniversityofWyoming/M2AENAD Lab - Documents/RESEARCH/multi-state/data/FVanalysis.RData")
```