---
title: "gender_analysis_final"
output: html_document
date: '2023-12-07'
---

This is an analysis based on the paper "The association of food parenting practices with adolescents’ dietary
behaviors differ by youth gender, but not by parent gender" by Deslippe et al., 2022

Redoing this with Yichen's dataset

```{r message=FALSE, warning=FALSE, results='hide'}
library(vroom)
library(plyr)
library(ggplot2)
library(psych)
library(tidyverse)
library(OpenMx)
library(dplyr)
library(lavaan)
library(semPlot)
library(knitr)
library(kableExtra)
library(GGally)
library(lavaanPlot)
library(lm.beta)
library(modelsummary)

#library(boot)
library(semTools)
source("~/Downloads/x.boot.r")  
library(emmeans)
library(rempsyc)
library(gridExtra)
library(fastDummies)
```
# Why
The previous notebook I tried to normalize the data. When I normalized the data the log function actually made everything worse. I am trying to fit the non-normal data this time. 

```{r message=FALSE, warning=FALSE, results='hide'}
df<-vroom("/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/2. data/iEOparent_food.csv")
#names(df)
```

## Mean center
```{r}
scaled_data <- 
  df %>%
  mutate(SSB_freq = scale(SSB, scale = FALSE),
         JUNK_freq = scale(Junk.foods, scale = FALSE),
         SWEET_freq = scale(Sugary.foods, scale = FALSE),
         FV_freq = scale(Fruits.vegetables, scale = FALSE),
         INDULGENCE = scale(Indulgence, scale = FALSE),
         EXPECATION = scale(Expectations, scale = FALSE),
         AVAILABILE = scale(Availability, scale = FALSE),
         MONITORING = scale(Monitoring, scale = FALSE),
         AUTONOMY = scale(Autonomy.Support, scale = FALSE),
         MODELING = scale(Modeling, scale = FALSE)
         )
```

child sex = sex, Q6.3
parent sex = Q6.11
ethnicity = Q6.18
```{r}
summary(as.factor(df$Q6_18))
names(df)
```
# Renaming factors for the tables
```{r}
df_factors<- df %>% 
  mutate(
    Marital_status = fct_recode(as.factor(Marital.status),
                      "Not married" = "1",
                      "Married" = "2"),
    Parent_gender = fct_recode(as.factor(Q6_11),
                      "Male" = "1",
                      "Female" = "2"),
    Ethnicity = fct_recode(as.factor(Q6_18),
                      "Male" = "1",
                      "Female" = "2"),
        Income = fct_recode(as.factor(Q6_17),
                      "Below $25,000" = "1",
                      "$65,000 - $84,999" = "4",
                      "$45,000 - $64,999" = "3",
                      "$85,000 or more" = "5",
                      "$25,000 - $44,999" = "2",
                      "Prefer not to answer" = "6"
                      ),
    child_sex = fct_recode(as.factor(Q6_3),
                      "Male" = "1",
                      "Female" = "2"
                      ),
    education = fct_recode(as.factor(Q6_14),
                      "4-year college, university degree or advanced degree" = "4",
                      "Some college or technical school" = "3",
                      "Received high school diploma or GED" = "2",
                      "Have not completed high school" = "1"
                      
                      ),
    ethnicity = fct_recode(as.factor(Q6_18),
                      "Hispanic or Latinx" = "1",
                      "Not Hispanic or Latinx" = "2"
                      
                      )
  )
```


# Making descriptive table
## Table 1. Sample demographics by parent sex
### Factors
```{r}
#(`Flipper length (mm)` = flipper_length_mm)

datasummary((`Marital status` = Marital_status) + Race+ (`Ethnicity` = ethnicity)+ Income + (`Child sex` = child_sex) + (`Food security` = Food.security) + (`Education` = education) ~ (`Parent gender` = Parent_gender) * Percent("col")+1*Percent("col"),
            data = df_factors,
            output = '/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/table1.docx')
```

### Continuous
```{r}
MeanSD <- function(x) paste0(round(mean(x, na.rm = TRUE),2),'(', round(sd(x, na.rm = TRUE),2), ')')

```

```{r}
datasummary((`Autonomy support` = Autonomy.Support) + Monitoring + Availability + Indulgence + Modeling + Expectations + (`SSB consumption frequency` = SSB) + (`Junk food consumption frequency` = Junk.foods) + (`Fruit and Vegetable consumption frequency` = Fruits.vegetables) + (`Sugary food consumption frequency` = Sugary.foods) + (`Independent eating occassion frequency` = iEO) ~ Parent_gender* (MeanSD) + 1*(MeanSD),
            data = df_factors,
            output = '/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/table1_b.docx')
```

### Check differences
```{r}
summary(df_factors$Parent_gender)
t.test(df_factors$iEO ~ df_factors$Parent_gender)
```
```{r}
mytable <- xtabs(~Parent_gender+Marital.status, data=df_factors)
summary(mytable) # chi-square test of indepedence
```

# Checking regressions against main paper for sanity
```{r}
check_FV_auto<-lm(Fruits.vegetables ~ Autonomy.Support +  Age + Race + Sex + Education + Food.security + Marital.status + iEO, data = df )
summary(check_FV_auto) # b values match the parent reporting parenting practice
```

## Basic model
food security, parent education, child sex, race/ethnicity, independent eating occasions (from covar analysis)
```{r}
mFV <-'FV_freq ~ INDULGENCE + EXPECATION + AVAILABILE + MONITORING + AUTONOMY + MODELING + Q6_11  + Race + Sex + Education + Food.security + iEO'
mSSB <-'SSB_freq ~ INDULGENCE + EXPECATION + AVAILABILE + MONITORING + AUTONOMY + MODELING + Q6_11  + Race + Sex + Education + Food.security + iEO'
mJUNK <-'JUNK_freq ~ INDULGENCE + EXPECATION + AVAILABILE + MONITORING + AUTONOMY + MODELING + Q6_11  + Race + Sex + Education + Food.security + iEO'
mSWEET <-'SWEET_freq ~ INDULGENCE + EXPECATION + AVAILABILE + MONITORING + AUTONOMY + MODELING + Q6_11  + Race + Sex + Education + Food.security + iEO'
```

## Refactor levels of race
```{r}
scaled_data$Race <- factor(scaled_data$Race, levels = c("Non-Hispanic White","Non-Hispanic Black", "Asian", "Hispanic", "Other races"))
```


## Summary
Basic models were not significant thus bootstrapping was not required
```{r}
models <- list(
  "Fruits and Vegetables"     = lm(mFV, data = scaled_data),
  "SSB"     = lm(mSSB, data = scaled_data),
  "Junk Foods"     = lm(mJUNK, data = scaled_data),
  "Sugary foods"     = lm(mSWEET, data = scaled_data)
)

modelsummary(
  models,
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}] {stars}",
  statistic = NULL,
  coef_omit = "Intercept",
  coef_rename = c("Q6_11" = "parent sex", "RaceHispanic" = "Hispanic", "RaceNon-Hispanic Black" = "Non-Hispanic Black","RaceNon-Hispanic White" = "Non-Hispanic White", "SexGirl" = "Child girl", "RaceAsian" = "Asian", "RaceOther races" = "Other races"), output = "/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/linearmodels_table.docx")
```
# Summary of CFA
INDULGENCE
MONITORING
iEO
```{r}
parent <- "INDULGENCE"
food <- "FV_freq"
my_string <- sprintf("this is my %s string", new)
```


```{r}
modelr <- function(parent,food){
  sprintf("
         # mediator, a path
         Q6_11 ~ a*%s+iEO

         # b path
        %s ~ b*Q6_11

         # direct effect 
         %s ~ cp * %s+iEO

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
        ",parent,food, food, parent)
}
```

```{r}
check <-sem(modelr("INDULGENCE","SSB_freq"), data = scaled_data, estimator = "MLM")
summary(check)
```

```{r}
food_list <- list("FV_freq","SSB_freq","JUNK_freq","SWEET_freq")

```

```{r}
sublist <- list()
for (y in food_list){
    model<-modelr("INDULGENCE",y)
    output <- sem(model, data = scaled_data, estimator = "MLM")
    sublist[[y]] <- list(output)
}
```


```{r}
modelsummary(
  c(sublist$FV_freq,
    sublist$SSB_freq,
    sublist$JUNK_freq, 
    sublist$SWEET_freq),
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}],{stars}",
  statistic = NULL,
  )

```
 
```{r}
sublist2 <- list()
for (y in food_list){
    model<-modelr("MONITORING",y)
    output <- sem(model, data = scaled_data, estimator = "MLM")
    sublist2[[y]] <- list(output)
}
```


```{r}
cm <- c('Q6_11 ~ MONITORING'    = 'Monitoring by parent gender',
        'FV_freq ~ Q6_11' = 'Fruit and vegetable intake by parent gender',
        'FV_freq ~ MONITORING' = 'Fruit and vegetable intake by monitoring',
        'SSB_freq ~ Q6_11' = 'SSB intake by parent gender',
        'SSB_freq ~ MONITORING' = 'SSB intake by monitoring',
        'JUNK_freq ~ Q6_11' = 'Junk food intake by parent gender',
        'JUNK_freq ~ MONITORING	' = 'Junk food intake by monitoring',
        'SWEET_freq ~ Q6_11' = 'Sugary food intake by parent gender',
        'SWEET_freq ~ MONITORING' = 'Sugary food intake by monitoring'
        )

modelsummary(
  c(sublist2$FV_freq,
    sublist2$SSB_freq,
    sublist2$JUNK_freq, 
    sublist2$SWEET_freq),
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}],{stars}",
  statistic = NULL,
  )
```


8/31/23

Random selection
```{r}
summary(as.factor(m_data$Q6_11))
f_data <-subset(scaled_data, scaled_data$Q6_11 == 2)
f_sub_data<-f_data[sample(nrow(f_data), 211), ]
m_data <-subset(scaled_data, scaled_data$Q6_11 == 1)

sub_data <- rbind(m_data, f_sub_data)
summary(as.factor(sub_data$Q6_11))
```

```{r}
sub_sublist <- list()
n = 100000
my_range <- 1:n
for (x in my_range){
    #separate females and randomly sample
    f_data <-subset(scaled_data, scaled_data$Q6_11 == 2)
    f_sub_data<-f_data[sample(nrow(f_data), 211), ]
    #separate males
    m_data <-subset(scaled_data, scaled_data$Q6_11 == 1)
    #recombine the male and subset female data
    sub_data <- rbind(m_data, f_sub_data)
    sub_data$Race <- factor(sub_data$Race, levels = c("Non-Hispanic White","Non-Hispanic Black", "Asian", "Hispanic", "Other races"))
    sub_model<-modelr("INDULGENCE","SSB")
    sub_output <- summary(sem(sub_model, data = sub_data, estimator = "MLM"))
    sub_sublist[[x]] <- list(sub_output$PE[11,])

}

null<-rep(0.05, each=n)
SSB_med_df<-bind_rows(sub_sublist, .id = "column_label")
t.test(SSB_med_df$pvalue, null)
SSB_med_df
```


## Refactor levels of race
```{r}
sub_data$Race <- factor(sub_data$Race, levels = c("Non-Hispanic White","Non-Hispanic Black", "Asian", "Hispanic", "Other races"))
```


## Summary
No difference to full sample
```{r}
sub_models <- list(
  "Fruits and Vegetables"     = lm(mFV, data = sub_data),
  "SSB"     = lm(mSSB, data = sub_data),
  "Junk Foods"     = lm(mJUNK, data = sub_data),
  "Sugary foods"     = lm(mSWEET, data = sub_data)
)

modelsummary(
  sub_models,
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}] {stars}",
  statistic = NULL,
  coef_omit = "Intercept",
  coef_rename = c("Q6_11" = "parent sex", "RaceHispanic" = "Hispanic", "RaceNon-Hispanic Black" = "Non-Hispanic Black","RaceNon-Hispanic White" = "Non-Hispanic White", "SexGirl" = "Child girl", "RaceAsian" = "Asian", "RaceOther races" = "Other races"), output = "/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/test_linearmodels_table.docx")
```


```{r}
food_list <- list("FV_freq","SSB_freq","JUNK_freq","SWEET_freq")

```

```{r}
sub_sublist <- list()
for (y in food_list){
    sub_model<-modelr("INDULGENCE",y)
    sub_output <- sem(sub_model, data = sub_data, estimator = "MLM")
    sub_sublist[[y]] <- list(sub_output)
}
```

```{r}
sub_model<-modelr("MONITORING","SSB_freq")
test_sum<-summary(sem(sub_model, data = sub_data, estimator = "MLM"))
test_sum$PE[,1]
test_sum$PE[11,]

```

```{r}
test_sum <-modelsummary(
  c(sub_sublist$FV_freq),
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}],{stars}",
  statistic = NULL,
  )
test_sum[1]
```
 
```{r}
sublist2 <- list()
for (y in food_list){
    model<-modelr("MONITORING",y)
    output <- sem(model, data = scaled_data, estimator = "MLM")
    sublist2[[y]] <- list(output)
}
```


```{r}
cm <- c('Q6_11 ~ MONITORING'    = 'Monitoring by parent gender',
        'FV_freq ~ Q6_11' = 'Fruit and vegetable intake by parent gender',
        'FV_freq ~ MONITORING' = 'Fruit and vegetable intake by monitoring',
        'SSB_freq ~ Q6_11' = 'SSB intake by parent gender',
        'SSB_freq ~ MONITORING' = 'SSB intake by monitoring',
        'JUNK_freq ~ Q6_11' = 'Junk food intake by parent gender',
        'JUNK_freq ~ MONITORING	' = 'Junk food intake by monitoring',
        'SWEET_freq ~ Q6_11' = 'Sugary food intake by parent gender',
        'SWEET_freq ~ MONITORING' = 'Sugary food intake by monitoring'
        )

modelsummary(
  c(sublist2$FV_freq,
    sublist2$SSB_freq,
    sublist2$JUNK_freq, 
    sublist2$SWEET_freq),
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}],{stars}",
  statistic = NULL,
  )
```


# 12/7/23
Found an issue with the model. It doesn't seem possible that sex is a mediator given that food parenting practices doesn't cause the person's sex. So two things:
1. Make sex the IV and food parenting practices the DV
2. Make sex the moderator of food parenting practices

## Return to the basic models
### Is there a difference in food intake by parent sex?

```{r}
modelsT <- list(
  "Difference in parent sex: Fruits and Vegetables"     = t.test(FV_freq ~ Q6_11, data = scaled_data),
  "Difference in parent sex: SSB"     = t.test(SSB_freq ~ Q6_11, data = scaled_data),
  "Difference in parent sex: Junk Foods"     = t.test(JUNK_freq ~ Q6_11, data = scaled_data),
  "Difference in parent sex: Sugary foods"     = t.test(SWEET_freq ~ Q6_11, data = scaled_data)
)
```

INDULGENCE + EXPECATION + AVAILABILE + MONITORING + AUTONOMY + MODELING
```{r}
modelsT2 <- list(
  "Difference in parent sex: Indulgence"     = t.test(INDULGENCE ~ Q6_11, data = scaled_data),
  "Difference in parent sex: Expectation"     = t.test(EXPECATION ~ Q6_11, data = scaled_data),
  "Difference in parent sex: Availability"     = t.test(AVAILABILE ~ Q6_11, data = scaled_data),
  "Difference in parent sex: Monitoring"     = t.test(MONITORING ~ Q6_11, data = scaled_data),
  "Difference in parent sex: Autonomy"     = t.test(AUTONOMY ~ Q6_11, data = scaled_data),
  "Difference in parent sex: Modeling"     = t.test(MODELING ~ Q6_11, data = scaled_data)
)
```




```{r}
pFV <- ggplot(scaled_data, aes(factor(Q6_11), Fruits.vegetables)) + 
  geom_violin() + 
  stat_summary(fun = "mean",
               geom = "crossbar", 
               width = 0.5,
               colour = "red") + 
  scale_x_discrete(breaks=c("1", "2"),
                      labels=c("Male", "Female")) +
  labs(title="Fruit and vegetable intakeby parent sex",
        x ="Parent Sex", y = "Frequency of fruit and vegetable intake")

pSSB <- ggplot(scaled_data, aes(factor(Q6_11), SSB)) + 
  geom_violin() + 
  stat_summary(fun = "mean",
               geom = "crossbar", 
               width = 0.5,
               colour = "red") + 
  scale_x_discrete(breaks=c("1", "2"),
                      labels=c("Male", "Female")) +
  labs(title="SSB intakeby parent sex",
        x ="Parent Sex", y = "Frequency of SSB intake")

pIND <- ggplot(scaled_data, aes(factor(Q6_11), Indulgence)) + 
  geom_violin() + 
  stat_summary(fun = "mean",
               geom = "crossbar", 
               width = 0.5,
               colour = "red") + 
  scale_x_discrete(breaks=c("1", "2"),
                      labels=c("Male", "Female")) +
  labs(title="Indulgent parenting by parent sex",
        x ="Parent Sex", y = "Indulgent parenting")

pMON <- ggplot(scaled_data, aes(factor(Q6_11), Monitoring)) + 
  geom_violin() + 
  stat_summary(fun = "mean",
               geom = "crossbar", 
               width = 0.5,
               colour = "red") + 
  scale_x_discrete(breaks=c("1", "2"),
                      labels=c("Male", "Female")) +
  labs(title="Parental monitoring by parent sex",
        x ="Parent Sex", y = "Monitoring")

```
# Display
```{r}
modelsummary(
  modelsT,
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}] {stars}",
  statistic = NULL,
  coef_omit = "Intercept",
  coef_rename = c("Q6_11" = "parent sex"))

modelsummary(
  modelsT2,
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}] {stars}",
  statistic = NULL,
  coef_omit = "Intercept",
  coef_rename = c("Q6_11" = "parent sex"))  

grid.arrange(pFV, pSSB,pIND, pMON, nrow = 2)
```
## Summary
Parental sex is weakly related to SSB and FV consumption.
Parental sex is related to indulgence, monitoring, and autonomy

# Mediation
Does indulgence, monitoring, autonomy mediate consumption of SSB or FV?
```{r}
parent <- "MONITORING"
food <- "SSB_freq"
```

Race + Sex + Education + Food.security + iEO
## Make dummy variables
```{r}
scaled_data<-dummy_cols(scaled_data, select_columns = c("Race" , "Sex" , "Education" , "Food.security"), remove_first_dummy = TRUE)

names(scaled_data)[names(scaled_data) == 'Race_Non-Hispanic Black'] <- 'RaceBlack'
names(scaled_data)[names(scaled_data) == 'Race_Asian'] <- 'RaceAsian'
names(scaled_data)[names(scaled_data) == 'Race_Hispanic'] <- 'RaceHispanic'
names(scaled_data)[names(scaled_data) == 'Food.security_Food secure'] <- 'FoodSecure'
names(scaled_data)[names(scaled_data) == 'Race_Other races'] <- 'RaceOther'
```

```{r}
modelr <- function(parent,food){
  sprintf("
         # mediator, a path the effect of sex on food parenting
         %s ~ a*Q6_11 + RaceBlack + RaceAsian + RaceHispanic + RaceOther + Sex_Girl + Education_2 + Education_3 + Education_4 + FoodSecure

         # b path, the effect of parenting on food intake
         %s ~ b*%s + iEO + RaceBlack + RaceAsian + RaceHispanic + RaceOther + Sex_Girl + Education_2 + Education_3 + Education_4 + FoodSecure

         # direct effect, the effect of sex on food intake
         Q6_11 ~ cp * %s + iEO + RaceBlack + RaceAsian + RaceHispanic + RaceOther + Sex_Girl + Education_2 + Education_3 + Education_4 + FoodSecure

         # indirect 
         ab := a*b
         
         # Total effects
         total := cp + (a*b)
        ",parent, food, parent, food)
}
```

```{r}
checkMonSSB <-sem(modelr("MONITORING","SSB_freq"), data = scaled_data, estimator = "MLM")
checkIndSSB <-sem(modelr("INDULGENCE","SSB_freq"), data = scaled_data, estimator = "MLM")
checkAutSSB <-sem(modelr("AUTONOMY","SSB_freq"), data = scaled_data, estimator = "MLM")

checkMonFV <-sem(modelr("MONITORING","FV_freq"), data = scaled_data, estimator = "MLM")
checkIndFV <-sem(modelr("INDULGENCE","FV_freq"), data = scaled_data, estimator = "MLM")
checkAutFV <-sem(modelr("AUTONOMY","FV_freq"), data = scaled_data, estimator = "MLM")
```


```{r}
 fct <- function(fit) {
    lavaan::standardizedSolution(fit)[, "est.std"]
  }
```
## Bootstrap to get p values and confInt
```{r}
checkMonSSB_boot <- bootstrapLavaan(checkMonSSB, R = 5000, FUN = fct, iseed = 8970)
checkIndSSB_boot <- bootstrapLavaan(checkIndSSB, R = 5000, FUN = fct, iseed = 8970)
checkAutSSB_boot <- bootstrapLavaan(checkAutSSB, R = 5000, FUN = fct, iseed = 8970)

checkMonFV_boot <- bootstrapLavaan(checkMonFV, R = 5000, FUN = fct, iseed = 8970)
checkIndFV_boot <- bootstrapLavaan(checkIndFV, R = 5000, FUN = fct, iseed = 8970)
checkAutFV_boot <- bootstrapLavaan(checkAutFV, R = 5000, FUN = fct, iseed = 8970)
```

## The p values of the important parts
1, 11, 22, 91, 92


### Monitoring SSB
```{r}
a<-checkMonSSB_boot[,1][!is.na(checkMonSSB_boot[,1])] 
b<-checkMonSSB_boot[,11][!is.na(checkMonSSB_boot[,11])] 
cp<-checkMonSSB_boot[,22][!is.na(checkMonSSB_boot[,22])] 
indirect<-checkMonSSB_boot[,91][!is.na(checkMonSSB_boot[,92])] 
Total<-checkMonSSB_boot[,11][!is.na(checkMonSSB_boot[,11])] 

# Values of the model coefficients
Betas <- standardizedSolution(checkMonSSB)[,"est.std"]

#Get the p-values for coefficient
P_vala <-mean( abs(a - mean(a, na.rm = T) )> abs( Betas[1]))
P_valb <-mean( abs(b - mean(b, na.rm = T) )> abs( Betas[11]))
P_valcp <-mean( abs(cp - mean(cp, na.rm = T) )> abs( Betas[22]))
P_valindirect <-mean( abs(indirect - mean(indirect, na.rm = T) )> abs( Betas[91]))
P_valtotal <-mean( abs(Total - mean(Total, na.rm = T) )> abs( Betas[92]))
SSBmonP<-c(P_vala, P_valb, P_valcp, P_valindirect, P_valtotal)
SSBmonP
#and some parametric bootstrap confidence intervals (2.5%, 97.5%) 
ConfIntA <- quantile(a, c(.025, 0.975), na.rm = TRUE)
ConfIntB <- quantile(b, c(.025, 0.975), na.rm = TRUE)
ConfIntCP <- quantile(cp, c(.025, 0.975), na.rm = TRUE)
ConfIntIndirect <- quantile(indirect, c(.025, 0.975), na.rm = TRUE)
ConfIntTotal <- quantile(Total, c(.025, 0.975), na.rm = TRUE)
SSBmonCI<-c(ConfIntA, ConfIntB, ConfIntCP, ConfIntIndirect, ConfIntTotal)
SSBmonCI
standardizedSolution(checkMonSSB)
```

### Monitoring FV
```{r}
a<-checkMonFV_boot[,1][!is.na(checkMonFV_boot[,1])] 
b<-checkMonFV_boot[,11][!is.na(checkMonFV_boot[,11])] 
cp<-checkMonFV_boot[,22][!is.na(checkMonFV_boot[,22])] 
indirect<-checkMonFV_boot[,91][!is.na(checkMonFV_boot[,92])] 
Total<-checkMonFV_boot[,11][!is.na(checkMonFV_boot[,11])] 

# Values of the model coefficients
Betas <- standardizedSolution(checkMonFV)[,"est.std"]

#Get the p-values for coefficient
P_vala <-mean( abs(a - mean(a, na.rm = T) )> abs( Betas[1]))
P_valb <-mean( abs(b - mean(b, na.rm = T) )> abs( Betas[11]))
P_valcp <-mean( abs(cp - mean(cp, na.rm = T) )> abs( Betas[22]))
P_valindirect <-mean( abs(indirect - mean(indirect, na.rm = T) )> abs( Betas[91]))
P_valtotal <-mean( abs(Total - mean(Total, na.rm = T) )> abs( Betas[92]))
FVmonP<-c(P_vala, P_valb, P_valcp, P_valindirect, P_valtotal)
FVmonP
#and some parametric bootstrap confidence intervals (2.5%, 97.5%) 
ConfIntA <- quantile(a, c(.025, 0.975), na.rm = TRUE)
ConfIntB <- quantile(b, c(.025, 0.975), na.rm = TRUE)
ConfIntCP <- quantile(cp, c(.025, 0.975), na.rm = TRUE)
ConfIntIndirect <- quantile(indirect, c(.025, 0.975), na.rm = TRUE)
ConfIntTotal <- quantile(Total, c(.025, 0.975), na.rm = TRUE)
FVmonCI<-c(ConfIntA, ConfIntB, ConfIntCP, ConfIntIndirect, ConfIntTotal)
FVmonCI
standardizedSolution(checkMonFV)
```
### Indugence FV
```{r}
a<-checkIndFV_boot[,1][!is.na(checkIndFV_boot[,1])] 
b<-checkIndFV_boot[,11][!is.na(checkIndFV_boot[,11])] 
cp<-checkIndFV_boot[,22][!is.na(checkIndFV_boot[,22])] 
indirect<-checkIndFV_boot[,91][!is.na(checkIndFV_boot[,92])] 
Total<-checkIndFV_boot[,11][!is.na(checkIndFV_boot[,11])] 

# Values of the model coefficients
Betas <- standardizedSolution(checkIndFV)[,"est.std"]

#Get the p-values for coefficient
P_vala <-mean( abs(a - mean(a, na.rm = T) )> abs( Betas[1]))
P_valb <-mean( abs(b - mean(b, na.rm = T) )> abs( Betas[11]))
P_valcp <-mean( abs(cp - mean(cp, na.rm = T) )> abs( Betas[22]))
P_valindirect <-mean( abs(indirect - mean(indirect, na.rm = T) )> abs( Betas[91]))
P_valtotal <-mean( abs(Total - mean(Total, na.rm = T) )> abs( Betas[92]))
FVIndP<-c(P_vala, P_valb, P_valcp, P_valindirect, P_valtotal)
FVIndP
#and some parametric bootstrap confidence intervals (2.5%, 97.5%) 
ConfIntA <- quantile(a, c(.025, 0.975), na.rm = TRUE)
ConfIntB <- quantile(b, c(.025, 0.975), na.rm = TRUE)
ConfIntCP <- quantile(cp, c(.025, 0.975), na.rm = TRUE)
ConfIntIndirect <- quantile(indirect, c(.025, 0.975), na.rm = TRUE)
ConfIntTotal <- quantile(Total, c(.025, 0.975), na.rm = TRUE)
FVIndCI<-c(ConfIntA, ConfIntB, ConfIntCP, ConfIntIndirect, ConfIntTotal)
FVIndCI
standardizedSolution(checkIndFV)
```
### Indugence SSB
```{r}
a<-checkIndSSB_boot[,1][!is.na(checkIndSSB_boot[,1])] 
b<-checkIndSSB_boot[,11][!is.na(checkIndSSB_boot[,11])] 
cp<-checkIndSSB_boot[,22][!is.na(checkIndSSB_boot[,22])] 
indirect<-checkIndSSB_boot[,91][!is.na(checkIndSSB_boot[,92])] 
Total<-checkIndSSB_boot[,11][!is.na(checkIndSSB_boot[,11])] 

# Values of the model coefficients
Betas <- standardizedSolution(checkIndSSB)[,"est.std"]

#Get the p-values for coefficient
P_vala <-mean( abs(a - mean(a, na.rm = T) )> abs( Betas[1]))
P_valb <-mean( abs(b - mean(b, na.rm = T) )> abs( Betas[11]))
P_valcp <-mean( abs(cp - mean(cp, na.rm = T) )> abs( Betas[22]))
P_valindirect <-mean( abs(indirect - mean(indirect, na.rm = T) )> abs( Betas[91]))
P_valtotal <-mean( abs(Total - mean(Total, na.rm = T) )> abs( Betas[92]))
SSBIndP<-c(P_vala, P_valb, P_valcp, P_valindirect, P_valtotal)
SSBIndP
#and some parametric bootstrap confidence intervals (2.5%, 97.5%) 
ConfIntA <- quantile(a, c(.025, 0.975), na.rm = TRUE)
ConfIntB <- quantile(b, c(.025, 0.975), na.rm = TRUE)
ConfIntCP <- quantile(cp, c(.025, 0.975), na.rm = TRUE)
ConfIntIndirect <- quantile(indirect, c(.025, 0.975), na.rm = TRUE)
ConfIntTotal <- quantile(Total, c(.025, 0.975), na.rm = TRUE)
SSBIndCI<-c(ConfIntA, ConfIntB, ConfIntCP, ConfIntIndirect, ConfIntTotal)
SSBIndCI
standardizedSolution(checkIndSSB)
```

### Autonomy SSB
```{r}
a<-checkAutSSB_boot[,1][!is.na(checkAutSSB_boot[,1])] 
b<-checkAutSSB_boot[,11][!is.na(checkAutSSB_boot[,11])] 
cp<-checkAutSSB_boot[,22][!is.na(checkAutSSB_boot[,22])] 
Autirect<-checkAutSSB_boot[,91][!is.na(checkAutSSB_boot[,92])] 
Total<-checkAutSSB_boot[,11][!is.na(checkAutSSB_boot[,11])] 

# Values of the model coefficients
Betas <- standardizedSolution(checkAutSSB)[,"est.std"]

#Get the p-values for coefficient
P_vala <-mean( abs(a - mean(a, na.rm = T) )> abs( Betas[1]))
P_valb <-mean( abs(b - mean(b, na.rm = T) )> abs( Betas[11]))
P_valcp <-mean( abs(cp - mean(cp, na.rm = T) )> abs( Betas[22]))
P_valAutirect <-mean( abs(Autirect - mean(Autirect, na.rm = T) )> abs( Betas[91]))
P_valtotal <-mean( abs(Total - mean(Total, na.rm = T) )> abs( Betas[92]))
SSBAutP<-c(P_vala, P_valb, P_valcp, P_valAutirect, P_valtotal)
SSBAutP
#and some parametric bootstrap confidence intervals (2.5%, 97.5%) 
ConfIntA <- quantile(a, c(.025, 0.975), na.rm = TRUE)
ConfIntB <- quantile(b, c(.025, 0.975), na.rm = TRUE)
ConfIntCP <- quantile(cp, c(.025, 0.975), na.rm = TRUE)
ConfIntAutirect <- quantile(Autirect, c(.025, 0.975), na.rm = TRUE)
ConfIntTotal <- quantile(Total, c(.025, 0.975), na.rm = TRUE)
SSBAutCI<-c(ConfIntA, ConfIntB, ConfIntCP, ConfIntAutirect, ConfIntTotal)
SSBAutCI
standardizedSolution(checkAutSSB)
```

### Autonomy FV
```{r}
a<-checkAutFV_boot[,1][!is.na(checkAutFV_boot[,1])] 
b<-checkAutFV_boot[,11][!is.na(checkAutFV_boot[,11])] 
cp<-checkAutFV_boot[,22][!is.na(checkAutFV_boot[,22])] 
Autirect<-checkAutFV_boot[,91][!is.na(checkAutFV_boot[,92])] 
Total<-checkAutFV_boot[,11][!is.na(checkAutFV_boot[,11])] 

# Values of the model coefficients
Betas <- standardizedSolution(checkAutFV)[,"est.std"]

#Get the p-values for coefficient
P_vala <-mean( abs(a - mean(a, na.rm = T) )> abs( Betas[1]))
P_valb <-mean( abs(b - mean(b, na.rm = T) )> abs( Betas[11]))
P_valcp <-mean( abs(cp - mean(cp, na.rm = T) )> abs( Betas[22]))
P_valAutirect <-mean( abs(Autirect - mean(Autirect, na.rm = T) )> abs( Betas[91]))
P_valtotal <-mean( abs(Total - mean(Total, na.rm = T) )> abs( Betas[92]))
FVAutP<-c(P_vala, P_valb, P_valcp, P_valAutirect, P_valtotal)
FVAutP
#and some parametric bootstrap confidence intervals (2.5%, 97.5%) 
ConfIntA <- quantile(a, c(.025, 0.975), na.rm = TRUE)
ConfIntB <- quantile(b, c(.025, 0.975), na.rm = TRUE)
ConfIntCP <- quantile(cp, c(.025, 0.975), na.rm = TRUE)
ConfIntAutirect <- quantile(Autirect, c(.025, 0.975), na.rm = TRUE)
ConfIntTotal <- quantile(Total, c(.025, 0.975), na.rm = TRUE)
FVAutCI<-c(ConfIntA, ConfIntB, ConfIntCP, ConfIntAutirect, ConfIntTotal)
FVAutCI
standardizedSolution(checkAutFV)
```

## Summary
Indulgent parenting mediates the relationship between parental sex and SSB intake
Indulgent parenting mediates the relationship between parental sex and FV intake
Monitoring parenting mediates the relationship between parental sex and SSB intake
Monitoring parenting mediates the relationship between parental sex and FV intake



```{r}
load(file = "/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/gender_analysis.RData")
```


```{r}
#save.image(file = "/Users/gracer/Library/CloudStorage/OneDrive-UniversityofWyoming/0. Lab/M2AENAD Lab - Documents/RESEARCH/multi-state/gender_paper/gender_analysis.RData")
```



